Manual of comparing optimal subsampling with model robust optimal subsampling method for poisson regression (standardised Multivariate Normal distribution)

### 2022-06-25 Manual.Rmd
updated theta values for the models
output clarification for OSMAC added

* As of now the model parameters and their respective response compositions are 
1. $\theta=[-1.0, 0.5, 0.1]$ generates data for Model 1 of $x_1,x_2$.
2. $\theta=[-1.0, 0.5, 0.5, 0.7]$ generates data for Model 2 of $x_1,x_2,x^2_1$.
3. $\theta=[-1.0, 0.5, 0.5, 0.3]$ generates data for Model 3 of $x_1,x_2,x^2_2$.
4. $\theta=[-1.0, 0.5, 0.5, 0.5, 0.5]$ generates data for Model 4 of $x_1,x_2,x^2_1,x^2_2$.

@@

>>>>

* As of now the model parameters and their respective response compositions are 
1. $\theta=[1.0, 0.5, 0.1]$ generates data for Model 1 of $x_1,x_2$.
2. $\theta=[1.0,-0.3, 0.3, 0.1]$ generates data for Model 2 of $x_1,x_2,x^2_1$.
3. $\theta=[1.0, 0.3,-0.3, 0.1]$ generates data for Model 3 of $x_1,x_2,x^2_2$.
4. $\theta=[1.0, 0.3, 0.3,-0.3, 0.1]$ generates data for Model 4 of $x_1,x_2,x^2_1,x^2_2$.

@@

* In **Identical_r0** for OSMAC Assumed Models there are two forms of outputs, 1) **OSMAC_output_New_x.Rdata** is when optimal sub-sampling probabilities are selected from the re-calculated probabilities of the Data Generating model, 2) **OSMAC_output_Old_x.Rdata** is when optimal sub-sampling probabilities are calculated based on the Assumed model. Throughout the simulation setup the later output is used.
